%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Wilson Resume/CV
% XeLaTeX Template
% Version 1.0 (22/1/2015)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Howard Wilson (https://github.com/watsonbox/cv_template_2004) with
% extensive modifications by Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{article} % Default font size

\input{structure.tex} % Include the file specifying document layout

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\title{Matthew Lewis} % Print the main header

%------------------------------------------------

\parbox{0.5\textwidth}{ % First block
\begin{tabbing} % Enables tabbing
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Address} \> 9 Tredwell Close \\
\> London, SW2 3JZ \\
\end{tabbing}}
\hfill % Horizontal space between the two blocks
\parbox{0.5\textwidth}{ % Second block
\begin{tabbing} % Enables tabbing
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Phone} \> (+44) 7909977421 \\ % Home phone
{\bf Email} \> \href{mailto:matthew@mglewis.co.uk}{matthew@mglewis.co.uk} \\ % Email address
{\bf Website} \> \href{http://www.mglewis.co.uk}{mglewis.co.uk}
\end{tabbing}}


%----------------------------------------------------------------------------------------
%	PERSONAL PROFILE
%----------------------------------------------------------------------------------------

\section{Personal Profile}

Enthusiastic software developer and systems engineer. Java experience amongst a wide variety of platforms, technologies and languages.

Likely to be found on evenings and weekends bouldering, playing football or at home undertaking personal programming projects.

%----------------------------------------------------------------------------------------
%	EMPLOYMENT HISTORY SECTION
%----------------------------------------------------------------------------------------

\section{Employment History}

\job
{2015 -}
{UBS}{https://www.ubs.com}{Authorised Officer}
{Software Engineer and Product Owner}
{\begin{itemize-noindent}
\setlength\itemsep{-0.2em}
\item Responsible for a portfolio of custom and 3rd party applications.
\item Managed team of offshore software developers.
\item Delivered IBM Business Process Manager to the UBS environment.
\end{itemize-noindent}
\textbf{Technologies:} Java, Jenkins, Linux, Git, Swift, Nexus, Shell, Oracle}

\job
{2013 - 2014}
{UBS}{https://www.ubs.com}{Non Officer}
{Software Engineer}
{\begin{itemize-noindent}
\setlength\itemsep{-0.2em}
\item Sucessfully delivered a complete stack upgrade of EMC Documentum 7.1.
\item Developed a number of high performance custom Java components.
\item Drove team adoption of best practices: VC, CI, Automated Testing, Release Management.
\end{itemize-noindent}
\textbf{Technologies:} Java, Jenkins, Linux, Solaris, Tomcat, Websphere, Ant, Shell, Oracle}

\job
{2011 - 2013}
{UBS}{https://www.ubs.com}{Graduate Trainee}
{Analyst}
{\begin{itemize-noindent}
\setlength\itemsep{-0.2em}
\item Developed VBA and Tableau reporting systems.
\item Designed and implemented a series of automated tools for use by remote support teams.
\end{itemize-noindent}
\textbf{Technologies:} VBA, Tableau, SQL, BASH, Atlassian Suite.}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\university
{2008 - 2011}
{University of Bristol}{http://www.bristol.ac.uk}
{2:1 Computer Science BSc (with Hons)}

\end{document}